---
title: "CET Perceptually Uniform Colour Maps"
author: "James Balamuta with material heavily taken from Peter Kovesi"
date: "`r Sys.Date()`"
bibliography: cet.bib
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CET Perceptually Uniform Colour Maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The [`cetcolor`](https://cran.r-project.org/package=cetcolor) package is designed
to bring to R the color maps created by [Peter Kovesi](http://peterkovesi.com/projects/colourmaps/) 
in @ARXIV:Kovesi:CETCOLORMAPS that avoid points of locally high colour contrast 
leading to the perception of false anomalies in your data when there is none.
The colour maps have been designed to avoid this phenomenon by having uniform 
perceptual contrast over their whole range.

This vignette attempts to summarize information presented at <http://peterkovesi.com/projects/colourmaps/>.

## Supported Colour Maps

There are 51 supported colour maps organised according to the attributes: 

- Linear
- Diverging
- Rainbow
- Cyclic
- Isoluminant

## Organisation of Colour Maps

Each colour map is named as follows:

```
                    linear_kryw_5-100_c67_n256
                      /      /    |    \    \
Colour map attribute(s)     /     |     \    Number of colour map entries
                           /      |      \
     String indicating nominal    |       Mean chroma of colour map
     hue sequence.                |
                              Range of lightness values
```

Moreover, the colour map name may contain cyclic shift information as well
as indicating whether it has been reversed by a flag.

```                                              
              cyclic_wrwbw_90-40_c42_n256_s25_r
                                          /    \
                                         /   Indicates that the map is reversed.
                                        / 
                   Percentage of colour map length
                   that the map has been rotated by.
```

## Colour Maps

### Linear

```{r fig.width = 7.5, fig.height = 8}
library("cetcolor")
display_cet_attribute(attribute = "linear")
```

### Diverging

```{r fig.width = 7.5, fig.height = 5}
display_cet_attribute(attribute = "diverging")
```

### Rainbow

```{r fig.width = 7.5, fig.height = 3.25}
display_cet_attribute(attribute = "rainbow")
```

### Cyclic


```{r fig.width = 7.5, fig.height = 4}
display_cet_attribute(attribute = "cyclic")
```

### Isoluminant


```{r fig.width = 7.5, fig.height = 3.25}
display_cet_attribute(attribute = "isoluminant")
```

### Overall

```{r fig.width = 7.5, fig.height = 12}
display_cet_all()
```
